\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{float}
\usepackage{xurl}

\setcounter{secnumdepth}{4}
\setlength{\belowcaptionskip}{-16pt}

\begin{document}

\title{Caselaw Access Project temporal analysis}

\author{Davide Carletti \and Francesco Tomaselli}
\authorrunning{D. Carletti \and F. Tomaselli}
\institute{University of Milan}
\maketitle

\begin{abstract}
    We here present an unsupervised methodology, based on topic modelling 
    and word embeddings, to study temporal trends and correlations
    in time of single and group of words in legal texts.    
    \keywords{Legal texts  \and Topic modelling \and Word embeddings}
\end{abstract}

\input{chapters/intro}
\input{chapters/research}
\input{chapters/experimental}
\input{chapters/conclusions}

\begin{thebibliography}{8}
\bibitem{harvard_caselaw}
Felix B. Chang, Erin McCabe and James Lee. ACL 2020. Mining the Harvard Caselaw Access Project.

\bibitem{glda}
Jagarlamudi Jagadeesh, Daum{\'e} III Hal and Udupa Raghavendra. ACL 2012. Incorporating Lexical Priors into Topic Models.

\bibitem{hist-words}
William L. Hamilton, Jure Leskovec, and Dan Jurafsky. ACL 2016. Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change. 

\bibitem{caselaw_query}
Jaromir Savelka, Huihui Xu and Kevin D. Ashley. ACL 2019. Improving Sentence Retrieval from Case Law for Statutory Interpretation.

\bibitem{argumentation_mining}
Raquel Mochales and Marie-Francine Moens. ACL 2011. Argumentation Mining.

\end{thebibliography}
\end{document}