\section{Research question and methodology}

The goal of the project is to analyze, from a collection 
of court decisions, the relevance of terms in time while 
also gathering information about possible correlations between 
them. The reasons to perform such a study are various, firstly, 
one could find interesting and unexpected correlations between terms, 
also, studying them in time could reveal a change of 
context of some words.\\
The research question is focused in particular on three main areas of interest:
narcotics, weapons and investigations. Thus, words related to this three main sets
are the most interesting ones to analyze.

In the first place, the methodology aimed to separate the original dataset in three main areas,
narcotics - weapons - investigations indeed; in this way, each document would have been assigned to one area.
Having documents divided per area of interest, it would have been possible to divide documents in temporal
periods and perform topic modelling and language modelling on the temporal subsections of the three areas. This
analysis would have allowed to directly confront the three sets also in a temporal way, showing differences
in the language and topics between words regarding drugs, narcotics and investigations respectively.
Some scientific literature has been explored and tested, based on the idea of Guided topic modelling (paragraph 3.2 -
Topic Modelling), but it has been soon discovered that the dataset comprehended many other topics other than the
three main areas of interest, and most importantly even when finding documents and terms regarding them,
it was pretty difficult to separate them in three distinct sets, because in reality the three sets are
interconnecting each other, being usually used together.

After this discovery, the methodology has been changed to a more general one: the dataset has been explored, by finding
the various topics and language models composing it, finding also semantic shift in words context between different
years and periods of time. After finding more generics topics, the discovered topics have been analyzed (and labelled),
and the ones regarding the initial three areas of interest have been chosen to been explored more in depth, to find
more meaningful results for the original research question.